---
title: "Vim Bindings"
author: "Risto Kaartinen"
date: "21 Nov 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Motions

`r lv `

<b>
```{r, echo=F}
df <- matrix("", 11, 14) %>% 
    data.frame(stringsAsFactors = F) %>% 
    setNames(rep("",14))


df[1,7] <- "&#9650;"
df[2,7] <- "gg"
df[3,7] <- "\\^b"
df[4,7] <- "\\^u"
df[5,7] <- "k"
df[7,7] <- "j"
df[8,7] <- "\\^d"
df[9,7] <- "\\^f"
df[10,7] <- "G"
df[11,7] <- "&#9660;"
df[6,1] <- "&#9668;"
df[6,2] <- "0"
df[6,3] <- "\\^"
df[6,4] <- "B"
df[6,5] <- "b"
df[6,6] <- "h"
df[6,7] <- ""
df[6,8] <- "l"
df[6,9] <- "e"
df[6,10] <- "w"
df[6,11] <- "E"
df[6,12] <- "W"
df[6,13] <- "$"
df[6,14] <- "&#9658;"
knitr::kable(df, align = "c")
```
</b>

### enter insert mode

* `i` before cursor
* `i` begin of line
* `a` append cursor
* `a` end of line
* `o` previous line
* `o` next line
* `s` sustitute character
* `s` substitute line (same as `cc`)
* `c` substitute end of line

### visual mode

* `v` select from cursor
* `V` select line
* `^v` ???

### Operators

* y yank
    * `yy` yank line
* c change
    * `C` change end of line
    * `cw` change rest of word
    * `ci[w/./)]` change in word/./)
* `p` paste after cursor
* `P` paste before cursor
* `
### Exercises

#### Remove quotes around text

"Remove quotes around this text" is `di"P2x`

#### Remove parentheses 

(Remove parentheses around this text) is `di)h2x`

#### Yank 2 first sentences

Yank first sentence. And second. But not the third. is `y2f.`

#### Make a increasing list

"101 This is an item." repeat sentence increasing the number.
On first row typ: qaYp[ctrl-a]q8@a

Result is:
101 This is an item.
102 This is an item.
103 This is an item.
104 This is an item.
105 This is an item.
106 This is an item.
107 This is an item.
108 This is an item.
109 This is an item.
110 This is an item.
111 This is an item.



{  }	beginning of previous, next paragraph
( )	beginning of previous, next sentence



    