---
title: "Vim Bindings"
author: "Risto Kaartinen"
date: "21 Nov 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Motions

<b>
```{r, echo=F}
df <- matrix("", 11, 14) %>% 
    data.frame(stringsAsFactors = F) %>% 
    setNames(rep("",14))


df[1,7] <- "&#9650;"
df[2,7] <- "gg"
df[3,7] <- "\\^b"
df[4,7] <- "\\^u"
df[5,7] <- "k"
df[7,7] <- "j"
df[8,7] <- "\\^d"
df[9,7] <- "\\^f"
df[10,7] <- "G"
df[11,7] <- "&#9660;"
df[6,1] <- "&#9668;"
df[6,2] <- "0"
df[6,3] <- "\\^"
df[6,4] <- "B"
df[6,5] <- "b"
df[6,6] <- "h"
df[6,7] <- ""
df[6,8] <- "l"
df[6,9] <- "e"
df[6,10] <- "w"
df[6,11] <- "E"
df[6,12] <- "W"
df[6,13] <- "$"
df[6,14] <- "&#9658;"
knitr::kable(df, align = "c")
```
</b>

### Up

* `gg` go to first line
* `^b` 1 page up
* `^u` 1/2 page up
* `k` one row up

### Backwards

* `0` beginning of line
* `^` first non-blank character
* `B` previous WORD
* `b` previous word

### Forward

* `l` one character right
* `e` end of word
* `w` beginning of next word
* `E` end of WORD
* `W` beginning of next WORD
* `$` end of line

### Enter Insert mode

* `i` before cursor
* `I` begin of line
* `a` append cursor
* `A` end of line
* `O` previous line
* `o` next line
* `s` substitute character
* `S` substitute line (same as `cc`)
* `C` substitute end of line

### Visual mode

* `v` select from cursor
* `V` select line
* `^v` ???

### Operators

* y yank
    * `yy` yank line
* c change
    * `C` change end of line
    * `cw` change rest of word
    * `ci[w/./)]` change in word/./)
* `p` paste after cursor
* `P` paste before cursor
* `
### Exercises

"Remove quotes around this text" is `di"P2x`

(Remove parentheses around this text) is `di)h2x`

Yank first sentence. And second. But not the third. is `y2f.`

eka, ""





    